Lens Modeling in \sw

### 2013-09-09 text/tex/spaghetti.tex
ideas for results section
added eR plots
time to go to sleep

\begin{figure}
\includegraphics[height=.3\vsize]{fig/spag6941.png} \\
\includegraphics[height=.3\vsize]{fig/spag7022.png} \\
\includegraphics[height=.3\vsize]{fig/spag6919.png}
\caption{Examples of Spaghetti input.  The models from these appear
  later in Figures \ref{fig:6941}, \ref{fig:7022} and
  \ref{fig:6919}. \label{fig:input-spag}}
\end{figure}

@@

The testing was done with a small number of volunteers ($N_v=4$) and a set of simulated configurations ($N_{sim}=30$) chosen to represent some typical configurations.

@@

The first test required the volunteers to accomplish 2 tasks: First to identify and distinguish lensed images from background light sources.
Second to come up with a logical ordering of the arrival time of those lensed images.

>>>>

\begin{figure}
  \centering
  \subfigure{\includegraphics[width=0.45\textwidth]{fig/sims/006941/input.png}}
  \subfigure{\includegraphics[width=0.45\textwidth]{fig/sims/007022/input.png}}
  \subfigure{\includegraphics[width=0.45\textwidth]{fig/sims/006919/input.png}}
%  \includegraphics[width=.45\textsize]{fig/spag6941.png}
%  \includegraphics[width=.45\textsize]{fig/spag7022.png}
%  \includegraphics[width=.45\textsize]{fig/spag6919.png}
  \caption{Examples of Spaghetti input.  The models from these appear
    later in Figures \ref{fig:6941}, \ref{fig:7022} and \ref{fig:6919}.
  \label{fig:input-spag}}
\end{figure}

@@

The testing was done with a small number of volunteers ($N_v=4$) and a set of simulated configurations ($N_{sim}=29$) chosen to represent some typical configurations.

@@

The first test required the volunteers to accomplish 2 tasks: First to identify and distinguish lensed images from background light sources.
Second to come up with a logical ordering of the arrival time of those lensed images.
It also tries to identify the problems volunteers encounter during modelling.
